### 2015-11-02 manuscript.Rnw
Added helpers + DJW grant support to acknowldegements

We would like to thank the organizers of the OpenTree of Life APIs hackathon
that was held at the University of Michigan, Ann Arbor, 15-19 September, 2014,
where the development of \texttt{rotl} was started. We would also like to thank
Scott Chamberlain (rOpenSci) for providing a thorough code review. FM was
supported by iDigBio, and therefore this material is based upon work supported
by the National Science Foundation’s Advancing Digitization of Biodiversity
Collections Program (Cooperative Agreement EF-1115210).

>>>>

We would like to thank the organizers of the OpenTree of Life APIs hackathon
that was held at the University of Michigan, Ann Arbor, 15-19 September, 2014,
where the development of \texttt{rotl} was started. We would also like to thank
Scott Chamberlain (rOpenSci) for providing a thorough code review and 
Shinichi Nakagawa and Alistair Senior for their help in developing the package's
meta-analysis vignette. DJW was supported by  NIH Grant R01-GM101352. SFM was
supported by iDigBio, and therefore this  material is based upon work supported
by the National Science Foundation’s Advancing Digitization of Biodiversity 
Collections Program (Cooperative Agreement EF-1115210).
